The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
update lcres fig cap

<!-- Figure: metrics by landcover resolution -->
(ref:lcres) Variation in multilayer network metrics as a function of changes in landcover resolution, a metric which we interpret as spatial scale. For each landcover resolution, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open). We examined how network metrics changed as a function of changes in spatial scale. A) Mean graph strength of individuals was weaker during the summer compared to the winter months. B) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter forage layer relevance at higher landcover resolutions. C) Similarity of landcover network layers between seasons (e.g. open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250 m and decrease in similarity for open layers at 250 m. Note that forage layer similarity is not shown because individuals did not interact in forage habitats greater greater than 30 m landcover resolution. D) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution.

>>>>

<!-- Figure: metrics by landcover resolution -->
(ref:lcres) Varying spatial scale in landcover resolution. For each landcover resolution, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open). A) Mean graph strength of individuals in winter forest and open habitats increased consistently while winter forage varied with a peak at 250 m and valley at 500 m. Individuals in summer layers had consistent weak connections. B) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter forage layer relevance at higher landcover resolutions. C) Similarity of landcover network layers between seasons (e.g. open summer compared to open winter) was relatively stable for forest and open, except for a sharp decrease in open at 100 m and 250 m. Note that layer similarity in summer forage is not shown because individuals did not interact at landcover resolutions greater than 30 m and therefore layer similarity could not be calculated. D) Mean connective redundancy across individuals showed a slight decreasing trend with increasing landcover resolution.
